---
title: 'Lab 7: Multiple linear regression intro'
author: "Alessandra Puig-Santana"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message =FALSE, warnings= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore the penguins dataset

Use the `GGally::ggpairs()` to create a pairs plot.
```{r}
ggpairs(penguins)
```

That is kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species
- bill_length_mm through body_mass_g
```{r}
penguins %>%
  select(species, bill_length_mm:body_mass_g) %>% # Selecting rows that include what we want. Select the first column, then from one variable : to the last one.
  ggpairs(aes(color = species)) # Color coded by species, this visualizes the comparisons, scatterplot is most important

mean <- mean(penguins$body_mass_g, na.rm = TRUE)
```
within groups, these look like linear relationships. 

## Multiple linear regression
 
We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguin body mass.

The different predictor variables we're going to try are:

- species
- flipper length
- sex
- bill depth

### Model body
Model body mass based on only flipper length and bill depth (bad idea.. there are important variables missing.)
```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins) # ~ means "as a function of"

# Call model by name to return only coefficients:
model_1

summary(model_1)
```
If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 51.54g on average. 

Actually -- we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex. 

```{r}
model_2 <- lm(data = penguins, body_mass_g ~ species + flipper_length_mm + sex)

# Let's check out the coefficients:
model_2

# the reference level penguin: Adelie (because it doesn't show up)
# the reference level for sex: female (because it doesn't show up)

# Try interpreting the coefficients for:
# flipper length: If everything else is held constant, we expect that for every mm increase in flipper length, penguin body mass is expected to increase by 20.02 g, on average.

# Gentoo penguin: If everything else is held constant, we expect that for 836.26 g heavier than adelie penguins on average.

# male penguin: On average, we expect male penguins to be 530.38 g heavier when compared to female penguins if all things are held constant. 
```

```{r}
# Data visualization on our model! 
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)
```


## A couple of ways to get & report MLR model outcomes 

Use broom::tidy() to get model coefficient info in a tidy data frame
```{r}
penguin_model2_coef <- tidy(model_2)

penguin_model2_coef
```

try to write inline code that spits out the coef for gentoo

`r penguin_model2_coef$estimate[4]`

## Look at the model diagnostics

Use the plot() function
```{r}
plot(model_2)

summary(model_2)
```
## Report the model outputs in a summary table 

Use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer:
```{r, results= "asis"}
# If using stargaze, include "results = "asis"" because it is already in HTML

stargazer(model_2, type = "html") # When you knit, it would come out AMAZING!

```

